a and generators

### 2022-05-06 documentos/generators.tex
ajax-loader hotness, oh yeah

\caption{Connection between rows and columns of $a$ and single qubit PCE
generators. We also include the corresponding 
labels $\mcG_\alpha$ of the generators.
% The rows or columns of $a$ and the diagrams of the generators are either 
% symmetric or anti-symmetric under reflection.
% \cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}

>>>>

\caption{
% Connection between rows and columns of $a$ and single qubit PCE
% generators. We also include the corresponding 
% labels $\mcG_\alpha$ of the generators. \cpnote{Nadie ha revisado el nuevo caption y la nueva figura con cuidado}
% \janote{Acá dejo mi propuesta para la caption:}
% \janote{A profound connection exists between the rows or columns of matrix $a$ 
% (in turn, $A$) [refer to \eref{eq:lambda:is:A:tau}] that diagonalizes 
% Choi's matrix of a PCE map and PCE generators $\mcG_\valpha$.
% For instance, if one takes the columns of $a$ and replace all -1's with 0's one
% is left with the sets of $\{\tau_\valpha\}$ of all single-qubit PCE generators.
% The converse procedure is also valid, one goes from the PCE generators 
% to the matrix $a$.}
% \cpnote{The connection between rows or columns of $a$ and single-qubit PCE
% generators is shown, with the 1s identified with preserved components and
% the $-1$s with deleted ones. For any number of particles, such simple relation 
% still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
\janote{The connection between rows or columns of $a$ and single-qubit PCE
generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
left with the sets $\{\tau_\alpha\}$ of preserved and erased components
by each $\mathcal G_\alpha$.
For any number of particles, such simple relation 
holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
\cpnote{The connection between rows or columns of $a$ and single-qubit PCE
generators $\mathcal G_\alpha$ is shown. One can identify the -1s of $a$ with
0s in the sets $\{\tau_\alpha\}$ of preserved and erased components
of each $\mathcal G_\alpha$.
For any number of particles, such simple relation 
holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
